---
title: 'Coursera - Developing Data Products : Week4 Assignment'
author: "Olga SILVA"
date: "24 octobre 2018"
output:
 slidy_presentation: default
runtime: shiny
---
## Create a Shiny Application
I wrote a shiny application, to make a wordcloud from a famous Winston Churchill's speech : "Blood, Toil, Tears and Sweat"

I wanted to use some other applications that we didn't see in the course. I use de shiny tutorials to inspire myself.

The user can choose the minimum frequency of words and the maximum number of words. Then, the plot will display the wordcloud, with a lot of colors

Here is the link to the shiny Server: https://olgasilva.shinyapps.io/WorldCloud/

***

## Create a Shiny Application
For the assignement, I also create these slides, to show you the application and the R Code. 

In the next slide you will find the R code who allows me to make the wordcloud, and the shiny application that you can use to test the application. 

To embedded the application I use the option runtime Shiny

***

## R CODE

```{r libraries, echo=TRUE}
library(shiny)
library(tm)
library(SnowballC)
library(wordcloud)
library(RColorBrewer)
```

```{r readtext, echo=TRUE}
text <- readLines("Winston_Churchill.txt")
docs <- Corpus(VectorSource(text))
docs <- tm_map(docs, content_transformer(tolower))
docs <- tm_map(docs, removeWords, stopwords("english"))
docs <- tm_map(docs, stripWhitespace)
set.seed(1234)

dtm <- TermDocumentMatrix(docs)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)
```

---
runtime: shiny
output: html_document
---
```{r ui, echo=TRUE}
ui <- fluidPage(
  # Application title
  titlePanel("Blood, Toil, Tears and Sweat - Wiston Churchill"),
  
  # Sidebar with a slider and selection inputs
  sidebarLayout(
    sidebarPanel(
      sliderInput("freq","Minimum Frequency:",min = 1,  max = 50, value = 15),
      sliderInput("max","Maximum Number of Words:",min = 1,  max = 300,  value = 100)
      
    ),
    mainPanel(
      plotOutput("graphplot")
    )
  )
)
```

```{r app, echo=TRUE}
server <- function(input, output) {
  output$graphplot <- renderPlot({
    
    wordcloud(words = d$word, freq = d$freq, min.freq = input$freq,
              max.words=input$max, random.order=FALSE, rot.per=0.35, 
              colors=brewer.pal(8, "Dark2"))
  })
}

shinyApp(ui = ui, server = server)
```